\documentclass[a4paper,12pt]{article}

\title{Exercise 4: Distance to the green box}
\author{Gruppe 6:\\Niels\\Troels\\Mark\\Kristian}

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[utf8]{inputenc}
\usepackage[british]{babel}
\usepackage{microtype}
\usepackage{underscore}

\usepackage{amsmath}

\usepackage{graphicx}

\usepackage[hidelinks]{hyperref}

\setlength{\parskip}{1ex}
\setlength{\parindent}{0pt}
\setlength{\parfillskip}{30pt plus 1 fil}

\begin{document}

\maketitle

\section{Estimating the field of view}

We need to know the FOV of our camera to be able to measure the distance to an
object with just one image.

See our program \texttt{findfov.cc} for the implementation.  It detects a green
box and uses its height in pixels in the image to calculate the field of view in
degrees.

Let
\begin{itemize}
\item $h_b$ be the known height of a box in centimeters;
\item $d$ be the known distance to the box;
\end{itemize}

and let
\begin{itemize}
\item $h_t$ be the total height of the image;
\item $v_c$ be the known vertical resolution of the camera in pixels;
\item $v_b$ be the measured vertical size of the box in pixels; and
\item $f$ be the field of view.
\end{itemize}

Then we consider the triangle with sides $a$, $b$, and $c$ and angles $A$, $B$,
and $C$, and calculate $f$:

\begin{align*}
  h_t &= \frac{v_c}{v_b} \cdot h_b\\
  a &= \frac{h_t}{2}\\
  b &= d\\
  c &= \sqrt{a^2 + b^2}\\
  A &= \arcsin \frac{a}{c}\\
  f &= 2 \cdot A
\end{align*}


\section{Distance from one image}

See our library function \texttt{distance_two_pictures} in \texttt{cam.cc} for
the implementation.

Let
\begin{itemize}
\item $h_b$ be the known height of the box in centimeters;
\item $v_c$ be the known vertical resolution of the camera in pixels;
\item $f$ be the known field of view;
\end{itemize}

and let
\begin{itemize}
\item $v_b$ be the measured vertical size of the box in pixels; and
\item $d$ be the distance to the box.
\end{itemize}

Then we consider the triangle with sides $a$, $b$, and $c$ and angles $A$, $B$,
and $C$, and calculate $d$:

\begin{align*}
  A &= \frac{f}{2}\\
  a &= h_b \cdot \frac{v_c}{v_b}\\
  c &= \frac{a}{\sin A}\\
  b &= c \cdot \cos A\\
  d &= b.
\end{align*}


\section{Distance from two images}

See our library function \texttt{distance_height_known} in \texttt{cam.cc} for
the implementation.

Let

\begin{itemize}
\item $d_b$ be the known travelled distance from the first position to the
second position; and
\end{itemize}

and let

\begin{itemize}
\item $v_{b_1}$ be the measured vertical size of the box in pixels from the
starting point;
\item $v_{b_2}$ be the measured vertical size of the box in pixels after having
travelled $d$ centimeters; and
\item $d$ be the distance to the box from the second position.
\end{itemize}

Then we use the relationship between the measured sizes to calculate $d$:

\begin{align*}
  d &= d_b * \frac{v_{b_1}}{v_{b_2} - v_{b_1}}
\end{align*}


\section{Detection of green box}

We're using the same algorithm as in our previous assigment, although with minor
tweaks in its magic constants.


\section{Accuracy}

\subsection{Testing}

\subsection{Standard deviation}

\end{document}
